---
title: "Assignment 06"
author: "Md Nakir Ahmed"
format: html
editor: visual
---

# 

# Load Libraries and Data

```{r}
library(quanteda)
library(quanteda.textmodels)
library(quanteda.textplots)
library(readr)
library(ggplot2)

summit <- read_csv("https://raw.githubusercontent.com/datageneration/datamethods/master/textanalytics/summit_11162021.csv")
sum_twt <- summit$text
toks <- tokens(sum_twt)
sumtwtdfm <- dfm(toks)
```

# Latent Semantic Analysis

```{r}
sum_lsa <- textmodel_lsa(sumtwtdfm)
summary(sum_lsa)
```

# Document-feature matrix and top hashtags

```{r}
tweet_dfm <- tokens(sum_twt, remove_punct = TRUE) %>%
  dfm()
tag_dfm <- dfm_select(tweet_dfm, pattern = "#*")
toptag <- names(topfeatures(tag_dfm, 50))
head(toptag, 10)
```

# Network Plot: Hashtags

```{r}
tag_fcm <- fcm(tag_dfm)
topgat_fcm <- fcm_select(tag_fcm, pattern = toptag)
textplot_network(topgat_fcm, min_freq = 50, edge_alpha = 0.8, edge_size = 5)
```

# Network Plot: Users

```{r}
user_dfm <- dfm_select(tweet_dfm, pattern = "@*")
topuser <- names(topfeatures(user_dfm, 50))
user_fcm <- fcm(user_dfm)
user_fcm <- fcm_select(user_fcm, pattern = topuser)
textplot_network(user_fcm, min_freq = 20, edge_color = "firebrick", edge_alpha = 0.8, edge_size = 5)
```

# Wordcloud: Early Inaugural Speeches

```{r}
dfm_inaug <- corpus_subset(data_corpus_inaugural, Year <= 1826) %>% 
  tokens(remove_punct = TRUE) %>% 
  tokens_remove(stopwords("english")) %>% 
  dfm() %>% 
  dfm_trim(min_termfreq = 10, verbose = FALSE)
set.seed(100)
textplot_wordcloud(dfm_inaug)
```

# Comparison Wordcloud by Presidents

```{r}
corpus_subset(data_corpus_inaugural, 
              President %in% c("Biden","Trump", "Obama", "Bush")) %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(stopwords("english")) %>%
  dfm() %>%
  dfm_group(groups = President) %>%
  dfm_trim(min_termfreq = 5, verbose = FALSE) %>%
  textplot_wordcloud(comparison = TRUE)
```

# Keywords-in-Context (KWIC) and X-Ray Plots

```{r}
data_corpus_inaugural_subset <- corpus_subset(data_corpus_inaugural, Year > 1949)
kwic(tokens(data_corpus_inaugural_subset), pattern = "american") %>% textplot_xray()
kwic(tokens(data_corpus_inaugural_subset), pattern = "trade") %>% textplot_xray()

tokens_inaugural <- tokens(data_corpus_inaugural_subset)
textplot_xray(
  kwic(tokens_inaugural, pattern = "american"),
  kwic(tokens_inaugural, pattern = "people"),
  kwic(tokens_inaugural, pattern = "trade")
)
```

------------------------------------------------------------------------

# 3. Compare Biden-Xi Summit Tweets and US Presidential Inaugural Speeches

The Biden-Xi summit tweets largely focus on geopolitical tensions, diplomacy, and U.S.–China relations, with frequent use of terms like “Biden,” “Xi,” “China,” and hashtags such as #uschina and #summit. The language is informal, immediate, and often emotionally charged, reflecting real-time public reaction.

In contrast, U.S. presidential inaugural speeches are formal, structured reflections of national values and political priorities. While early speeches emphasized unity, liberty, and the Constitution, modern ones address broader issues like security, economy, and climate change. Despite evolving language and tone, recurring themes like democracy, nationhood, and the American people persist. Together, the datasets illustrate how public discourse and presidential rhetoric both reflect and shape national identity over time.

------------------------------------------------------------------------

# 4. What is Wordfish?

Wordfish is an unsupervised text scaling method used to estimate the position of documents (like political speeches or tweets) along a single latent dimension, such as ideology. It analyzes word frequencies to place texts on a scale without needing predefined labels.

In R, it's implemented via `textmodel_wordfish()` in the `quanteda.textmodels` package and outputs each document’s position (`theta`) and word influence (`beta`) to help interpret the underlying topic or stance.

------------------------------------------------------------------------

# 
